---
title: "R-Test2"
date: "Sunday, July 19, 2015"
output: html_document
---

ssignment
----------------------------------------------------------------------------

"You should take the data, and create a data frame with a subset of the columns
(and if you like rows) in the dataset. You should include the column that indicates edible or poisonous and three or
four other columns. You should also add meaningful column names and replace the abbreviations used in the
data—for example, in the appropriate column, “e” might become “edible.” Your deliverable is the R code to
perform these transformation tasks"




**Part 1**
Create a variable to read the file, and assign column headers

```{r}

shrooms <- read.delim("agaricus-lepiota.csv",header = FALSE, sep = ",")
colnames(shrooms) = c("classDistribution","capShape","capSurface","capColor", "bruises", "odor","gillAttachment","gillSpacing", "gillSize", "gillColor", "stalkShape","stalkRoot","stalkSurfaceAboveRing", "stalkSurfaceBelowRing","stalkColorAboveRing","stalkColorBelowRing","veilType","veilColor","ringNumber","ringType","sporePrintColor","population","habitat")
```


**Part 2**
Load the PLYR package to speed up data manipulation, using the revalue function
```{r, echo=FALSE}
library(plyr)
```

**Part 3**
Replace abbreviated values, based on a match, with more readable names

```{r}
shrooms$classDistribution <-revalue(shrooms$classDistribution, c("p" = "poisonous", "e" = "edible"))
shrooms$capShape <-revalue(shrooms$capShape, c("b" = "bell",
"c" = "conical",
"x" = "convex",
"f" = "flat",
"s" = "sunken",
"k" ="knobbed"
))
shrooms$capSurface <-revalue(shrooms$capSurface, c("f" = "fibrous",
"g" = "grooves",
"y" = "scaly",
"s" = "smooth"))
shrooms$capColor <-revalue(shrooms$capColor, c("n" = "brown",
"b" = "buff",
"c" = "cinnamon",
"g" = "gray",
"r" = "green",
"u" = "purple",
"e" = "red",
"w" = "white",
"y" = "yellow",
"p" = "pink"))
shrooms$bruises <-revalue(shrooms$bruises, c("t" = "bruises",
"f" = "noBruises"))
shrooms$odor <-revalue(shrooms$odor, c("a" = "almond",
"l" = "anise",
"c" = "creosote",
"y" = "fishy",
"f" = "foul",
"m" = "musty",
"n" = "none",
"p" = "pungent",
"s" = "spicy"))
```

**Part 4**

Display 5 columns of data, and some rows
```{r}
shrooms[1:5,1:5]
```
