---
title: "R-Test3"
date: "Saturday, July 25, 2015"
output: html_document
---

Assignment
----------------------------------------------------------------------------

"Choose an interesting dataset and use R graphics to describe thdata. You may
use base R graphics, or a graphics package of your choice. You should include at least one example of each of the
following:
.  histogram
.  boxplot
.  scatterplot
Do the graphics provide insight into any relationships in the data?"

**Answer**
Yes, the graphics do provide insight, and show the relationship between complaints and total number of officers involved. As seen in the scatterplot, the largest
grouping of complaints occurred when there were around 2000 total officers involved. Bronx patrol group had the highest number of complaints, while the "other patrol services"
and "special operations division" had the fewest complaints.

**Load data and required Packages**
```{r}
#install.packages("ggplot2")
#install.packages("RColorBrewer")
require(ggplot2)
complaints <- read.csv(url("http://data.cityofnewyork.us/api/views/js82-9nvz/rows.csv?accessType=DOWNLOAD"))
```

**Histogram**

```{r}
ggplot(data = complaints) + geom_histogram(aes(x=Complaints.Count))
```

**Boxplot**

```{r}
boxplot(complaints$Number.Of.Subject.Officers)
```

**Scatterplot**
This scatterplot shows the total number of complaints over the time frame of the data ()

```{r}
plot(complaints$Complaints.Count ~ complaints$Number.Of.Subject.Officers)
```

**Enhanced Scatterplot**
This enahnced Scatterplot adds color, a legend, and facets to the mix. It is more helpful is showing a relationship to the data, as it breaks down
the complaints per officer, per department year over year.

```{r}
qplot(Number.Of.Subject.Officers,Complaints.Count, data = complaints, color = Precinct...Command, facets = Year ~.)
```
