---
title: "R-Test1"
date: "Sunday, July 12, 2015"
output: html_document
---

Assignment
----------------------------------------------------------------------------

"R has built in functions for choose() and factorial(). Your task is to write your own variation of the choose()function, that does not use either of these functions"


There were two parts to this assignment
- Create our own factorial and choose code
- Create a function that takes user input and run it through the function

**Part 1**
Since we were not allowed to use factorial, my version of factorial is as such:

```{r}
a <-1

for(i in 1:12){
  a = a * i
}
print(a)
```


**Part 2**
My version of the choose and factorial code, combined into a single function:
```{r, echo=FALSE}
calculate.choose <- function (val1, val2){

n <-1
r <-1
d <-1
difference = val1 - val2

for(i in 1:val1){
  n = n * i

}

for(j in 1:val2){
	r = r * j

}

for(k in 1:difference){
	d = d * k

}

final <- n/(d * r)
print(final)

}
```

I can validate this code works, by passing in the values from the homework example. I used 5 as r, and 3 as n. The answers is found below:

```{r}
calculate.choose(5, 3)
```


